doe-pkgs-analysis

### 2021-09-10 analysis/doe-pkgs-analysis.Rmd
tidy the author data.

# create function to extract the depends, imports, and suggests 
get_pkg <- function(var){
  # select only the package name and depends/imports/suggests
  tmp_df <- pkg_tidy %>%
    select(L2, author_ulrike, var) %>%
    # separate every depends/imports/suggests
    cSplit(var, sep = " ,")

@@

# bind data frames
pkg_edges <- rbind(depend_df, import_df, suggest_df) %>%
  select(-doe_pkg_related) %>%
  select(pkg, L2, type, author_ulrike)

@@

# create nodes from the two previous dataframe
pkg_nodes <- full_join(from, to, by = c("L2" = "pkg")) %>%
  left_join(pkg_tidy, by = "L2") %>%
  select(L2, author_ulrike)

pkg_nodes_full <- pkg_tidy%>%
  select(L2)

@@

## Create network using geomnet

```{r}
set.seed(12345)
ggplot(pkg_net, aes(from_id = L2, to_id = pkg)) +
  geom_net(layout.alg = "kamadakawai",
    size = 2, 
    labelon = TRUE, 
    vjust = -0.6, 
    directed = FALSE, 
    fontsize = 2)
```

Note: This method results error, and only works with the edges only. However, even with the example data, the error stil occurs (may be the bug in the package?)

```{r}
## Example of issue in geomnet

edges <- madmen$edges
nodes <- madmen$vertices

madmen_net <- fortify(as.edgedf(edges), nodes)

set.seed(12345)
ggplot(madmen_net, aes(from_id = from_id, to_id = to_id)) +
  geom_net(layout.alg = "kamadakawai",
    size = 2, 
    labelon = TRUE, 
    vjust = -0.6, 
    directed = FALSE, 
    fontsize = 2)
```

@@

set.seed(1234567)
plot(routes_igraph, edge.arrow.size = 0.2, layout = layout_with_graphopt)
```
Notes: The label overlapped, it is hard to see the network

@@

```{r}
ggraph(routes_tidy, layout = "stress") + 
  geom_edge_link(aes(color = type),
                 arrow = arrow(length = unit(1, 'mm')), 
                 end_cap = circle(1, 'mm')) + 
  geom_node_point(aes(color = author_ulrike)) + 
  scale_color_manual(values = c("#707B7C", "#F5B041"), labels = c("no", "yes")) +
  geom_node_text(aes(label = name), repel = TRUE, size = 2) +
  theme_graph()

@@

forceNetwork(Links = edges_d3, Nodes = nodes_d3, Source = "from", Target = "to", 
             NodeID = "L2", Group = "author_ulrike", 
             opacity = 1, fontSize = 16, zoom = TRUE)
```

>>>>

# create function to extract the depends, imports, and suggests 
get_pkg <- function(var){
  # select only the package name and depends/imports/suggests
  tmp_df <- pkg_tidy %>%
    select(L2, author, var) %>%
    # separate every depends/imports/suggests
    cSplit(var, sep = " ,")

@@

# bind data frames
pkg_edges <- rbind(depend_df, import_df, suggest_df) %>%
  select(-doe_pkg_related) %>%
  select(pkg, L2, type, author)

@@

# create nodes from the two previous dataframe
pkg_nodes_tmp <- full_join(from, to, by = c("L2" = "pkg")) %>%
  left_join(pkg_tidy, by = "L2") %>%
  select(L2, author)

# tidy author 
aut_tidy <- pkg_nodes_tmp %>%
  separate_rows(author, sep=", (?=[A-Z])") %>%
  filter(!str_detect(author, "ctb") & !str_detect(author, "National") & !str_detect(author, "Columbia"))

aut_tidy$author <- rm_angle(aut_tidy$author, replacement = "")
aut_tidy$author <- rm_square(aut_tidy$author, replacement = "")

aut_tidy <- aut_tidy %>%
  mutate(author = ifelse(str_detect(author, "Contributor"), "Yves Deville",
                         ifelse(str_detect(author, "based"), "Ernesto Barrios",
                                ifelse(str_detect(author, "contributions"), "John Lawson", author))))

aut_group <- aut_tidy %>%
  group_by(author) %>%
  count() %>%
  arrange(desc(n)) %>%
  mutate(aut_gr = as.factor(ifelse(n > 1, author, "other")))

aut_tidy_join <- left_join(aut_tidy, aut_group, by = "author") %>%
  group_by(L2) %>%
  arrange(desc(n), .by_group = TRUE)

pkg_nodes <- aut_tidy_join[!duplicated(aut_tidy_join$L2), ] %>%
  select(L2, aut_gr)

# nodes for all of the author in DoE packages
pkg_nodes_full <- pkg_tidy%>%
  select(L2)

@@

@@

# set.seed(1234567)
# plot(routes_igraph, edge.arrow.size = 0.2, layout = layout_with_graphopt)
# Notes: The label overlapped, it is hard to see the network
```

@@

```{r}
ggraph(routes_tidy, layout = "stress") + 
  geom_edge_link(aes(color = type),
                 arrow = arrow(length = unit(1, 'mm')), 
                 end_cap = circle(1, 'mm')) + 
  geom_node_point(aes(color = aut_gr)) + 
  geom_node_text(aes(label = name), repel = TRUE, size = 2) +
  theme_graph()

@@

forceNetwork(Links = edges_d3, Nodes = nodes_d3, Source = "from", Target = "to", 
             NodeID = "L2", Group = "aut_gr", 
             opacity = 1, fontSize = 16, zoom = TRUE)
```
